\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}

\title{Pre-Production Document for Capstone Project}
\author{Abdullah J. Rowaished}
\date{22 June 2019}

\begin{document}
\maketitle
\section{VR Medieval Farming Simulator}
The player will be set into a farming environment and will plant seeds into the ground. He will consult the botany book in order to figure out the correct proportions of fertilizer, soil and water. Various farming tools in the vicinity will be used in unique ways and combinations to achieve this. If the plants weren't taken care of properly and weren't harvested in time the crops quality may be affected. The randomized existence of rain or drought will affect the outcome.
\section{Features}
\subsection{3D Models}
Using Blender, a set of 3D models shall be created.
\subsubsection{Tools}
A bunch of farming tools will be modeled for players' use via Blender.
\begin{enumerate}
\item \textbf{Scythe}
\item \textbf{Hoe}
\item \textbf{Basket}
\item \textbf{Bucket}
\item \textbf{Watering Pot}
\item \textbf{Animal Trap}
\end{enumerate}
\subsubsection{Produce}
Produce such as fruits and vegetables shall be modeled using Blender also.
\begin{enumerate}
\item \textbf{Apple}, its \textbf{Apple Seed} and \textbf{Apple Tree}
\item \textbf{Pear}, its \textbf{Pear Seed} and \textbf{Pear Tree}
\item \textbf{Orange}, its \textbf{Orange Seed} and \textbf{Orange Tree}
\item \textbf{Wheat}, its \textbf{Grain} and \textbf{Wheat Bushel}
\item \textbf{Melon}, its \textbf{Melon Seed} and \textbf{Melon Growth}
\end{enumerate}
\subsubsection{Environment}
A farm shall be modeled using Blender, alongside its pests.
\begin{itemize}
\item \textbf{Wooden Fence} sets boundary of the farm
\item \textbf{Soil} Ploughable ground
\item \textbf{Ploughed Soil} Ploughed ground
\item \textbf{Skybox} Atmosphere of the farm
\item \textbf{Groundhog} Animal acting as pestilence
\end{itemize}
\subsection{Animations}
\begin
\subsection{Sound Effects}

\section{Game Loop}
\end{document}